\documentclass[a4paper,12pt]{article}

\usepackage{url}
\usepackage{parskip}
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[unicode, draft=false]{hyperref}

\newcolumntype{C}{>{\centering\arraybackslash}X}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

\hbadness=10000

\newenvironment{itemList}[3][]
    {
    \noindent\hspace{1em}\textbf{#2}\hfill#3\\[3.75pt]
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=3pt,label={},#1]
    }
    {
    \end{itemize}
    \end{minipage}
    }

\newcommand{\listSubHeading}[1]{
    \item[] \noindent\hspace{-1em}\textit{#1}
    }

\begin{document}

\pagestyle{empty}

\begin{tabularx}{\linewidth}{@{} C @{}}
    \Huge{Nguyen Ngoc Duy Bao} \\[7.5pt]
    \href{tel:+84396370405}{\raisebox{-0.05\height}\ +84 396-370-405} \ $|$\
    \href{mailto:foxeiz2004@gmail.com}{\raisebox{-0.05\height}\ foxeiz2004@gmail.com} \ $|$\
    \href{https://github.com/foxeiz}{\raisebox{-0.05\height}\ github.com/foxeiz} \ $|$\
    \href{https://linkedin.com/in/foxeiz}{\raisebox{-0.05\height}\ linkedin.com/in/foxeiz}
\end{tabularx}

\section{Summary}
A IT student seeking Software Engineering internship opportunities. I have good experience with back-end development through personal projects and coursework. I've built several APIs, worked with different databases, and improved server performance. \\
I write clean code that's easy to maintain and enjoy working in teams. I'm eager to learn new technologies and grow my skills in software development.

\section{Technical Skills}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=4pt, label={}]
    \item \textbf{Programming Languages:} Python, C\#, Go, JavaScript, Lua
    \item \textbf{Frameworks \& Libraries:} Flask, fastapi, ASP.NET, Next.js, Express.js
    \item \textbf{Databases:} MongoDB, MySQL, SQLite
    \item \textbf{Tools \& Technologies:} Git, Docker, Linux (Fedora), Ruff
\end{itemize}

\section{Key Projects}

\begin{itemList}{Nameless*}{\href{https://github.com/team-nameless/nameless-discord-bot/}{Github}}
    \item -- A Discord bot developed using meta-programming techniques and asynchronous programming in Python.
    \item -- Utilized Ruff for code linting and uv for dependency management.
\end{itemList}

\begin{itemList}{proxy-server}{\href{https://github.com/foxeiz/proxy-server/}{Github}}
    \item -- Developed a custom proxy server, focusing on modifying HTTP requests and responses based on user-defined rules.
    \item -- Used Quart for asynchronous web handling.
\end{itemList}

\begin{itemList}{mpv-discord-cplugin}{\href{https://github.com/foxeiz/mpv-discord-cplugin/}{Github}}
    \item -- Developed a custom plugin for MPV media player, integrating Discord Rich Presence.
    \item -- Used C for scripting and Lua JIT for IPC communication with Discord.
\end{itemList}

\begin{itemList}{dca (maintainer)}{\href{https://github.com/foxeiz/dca/}{Github}}
    \item -- Maintain and improve a real-time audio streaming solution for Discord.
    \item -- Focused on audio processing, streaming and performance tuning.
\end{itemList}

\newpage
\section{Academic Achievements}

\begin{itemList}{ecommerce-prj}{\href{https://github.com/FoxeiZ/ecommerce-prj/}{Github}}
    \listSubHeading{\href{https://github.com/FoxeiZ/ecommerce-prj/graphs/contributors}{\textcolor{black}{Lead Developer}}}
    \item -- Built a simple full-stack e-commerce application.
    \item -- Used ASP.NET, Bootstrap5, and Microsoft SQL Server.
\end{itemList}

\begin{itemList}{huoo}{\href{https://github.com/foxeiz/huoo/}{Github}}
    \listSubHeading{\href{https://github.com/FoxeiZ/huoo/graphs/contributors}{\textcolor{black}{Lead Developer}}}
    \item -- A cross-platform music application for a school assignment.
    \item -- Used Flutter for the front-end.
    \item -- Implemented user authentication using Firebase and SQLite for data storage.
\end{itemList}

\begin{itemList}{huoo-api}{\href{https://github.com/foxeiz/huoo-api}{Github}}
    \listSubHeading{\href{https://github.com/FoxeiZ/huoo-api/graphs/contributors}{\textcolor{black}{Lead Developer}}}
    \item -- The back-end API for the huoo music application.
    \item -- Used FastAPI for building the API and Firestore for data storage.
\end{itemList}

\begin{itemList}{CoffeShopManagerWebsite-BE}{\href{https://github.com/foxeiz/CoffeShopManagerWebsite-BE/}{Github}}
    \item -- A back-end application for a coffee shop management system.
    \item -- Mainly focused on CRUD, inventory \& order management, user authentication.
\end{itemList}


\section{Education}
\begin{itemList}{HUFLIT}{\href{https://huflit.edu.vn/}{Website}}
    \item 2022 - Present \hfill  (2.81/4.0)\\
\end{itemList}

\section{Open Source Contributions}
\begin{itemList}{extensions-source}{\href{https://github.com/keiyoushi/extensions-source}{GitHub}}
    \item Contributed 5 commits in bug fixes and feature enhancements
    \item Participated in community discussions and issue reporting
\end{itemList}

\newpage
\section{Skills}
\begin{itemList}[itemsep=5pt]{Hard Skills}{}
    \item -- \textbf{Version Control:} Git, GitHub
    \item -- \textbf{Debugging:} Proficient in using debugging tools
    \item -- \textbf{Databases:} Experience with MongoDB, MySQL, and SQLite
    \item -- \textbf{API Development:} Flask, FastAPI, Express.js
\end{itemList}

\begin{itemList}[itemsep=5pt]{Soft Skills}{}
    \item -- \textbf{Problem Solving:} Strong analytical skills
    \item -- \textbf{Teamwork:} Effective collaboration in team environments
    \item -- \textbf{Communication:} Clear and concise communication skills
    \item -- \textbf{Adaptability:} Quick learner, able to adapt to new technologies
\end{itemList}

\section{Languages}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=4pt, label={}]
    \item \textbf{English:} Intermediate (B1)
    \item \textbf{Vietnamese:} Native
\end{itemize}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
